Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-13 cikm2016/intro.tex
minor edits to related work and contributions.

\begin{itemize}
\setlength\itemsep{0em}
\item By analyzing an online corpus, we provide evidence that practical date parsing requires the ability to recognize hundreds of formats;
\item We show how to extend prior work on Minimum Descriptive Length structure extraction to generate a freely available date format domain language with over 95\% accuracy;
\item We describe a second Natural Language Processing technique for generating the same date format domain language with similar accuracy. We describe how the basic algorithm is extended to support grammar variants and constraints unique to date formats. The parsing algorithm is extended to compute an overall dominant pattern over a data column;
\item We provide evidence that the development of multiple, independent parsing algorithms provides an effective means of cross-validation on large corpora;
\item We describe some limitations of this domain language that would improve its utility.
\end{itemize}
%% vidya: don't think we need this.
%% richard: It's kind of traditional in the DB community, but we can just leave it commented out - and put it back if they complain!
%\subsection{Organization}
%The rest of this paper is organized as follows: The next section provides background information for the problem space. The following two sections describe the two different algorithms, one using Minimum Descriptive Length and the other using Natural Language Processing. In section V, we evaluate the algorithms on a corpus of 30K columns, both by sampling the outputs manually and then by using the algorithms to validate each other. We then discuss related work in section VI, future work in section VII and conclude in section VIII.

>>>>

\begin{itemize}
\setlength\itemsep{0em}
\item By analyzing an online corpus, we provide evidence that practical date parsing requires the ability to recognize hundreds of formats.
\item We show how to extend prior work on Minimum Descriptive Length structure extraction to generate a freely available date format domain language with over 95\% accuracy.
\item We describe a second Natural Language Processing technique for generating the same date format domain language with similar accuracy. We describe how the basic algorithm is extended to support grammar variants and constraints unique to date formats. The parsing algorithm is extended to compute an overall dominant pattern over a data column.
\item We provide evidence that the development of multiple, independent parsing algorithms provides an effective means of cross-validation on large corpora.
\item We describe some limitations of this domain language that would improve its utility.
\end{itemize}
%% vidya: don't think we need this.
%% richard: It's kind of traditional in the DB community, but we can just leave it commented out - and put it back if they complain!
%\subsection{Organization}
%The rest of this paper is organized as follows: The next section provides background information for the problem space. The following two sections describe the two different algorithms, one using Minimum Descriptive Length and the other using Natural Language Processing. In section V, we evaluate the algorithms on a corpus of 30K columns, both by sampling the outputs manually and then by using the algorithms to validate each other. We then discuss related work in section VI, future work in section VII and conclude in section VIII.

### 2016-05-13 cikm2016/relatedwork.tex
minor edits to related work and contributions.

Various approaches have been described for deriving regular expressions, and a good overview is provided by Li et al. in their paper on the ReLIE system for deriving regular expressions given a starting expression provided by a domain expert~\cite{Li:2008}. The Minimum Descriptive Length technique first described in Rissanen~\cite{Rissanen:1978} was used in~\cite{Raman:2001} to generate regular expressions.

>>>>

Various approaches have been described for deriving regular expressions, and a good overview is provided by Li \textit{et al.} in their paper on the ReLIE system for deriving regular expressions given a starting expression provided by a domain expert~\cite{Li:2008}. The Minimum Descriptive Length technique first described in Rissanen~\cite{Rissanen:1978} was used in~\cite{Raman:2001} to generate regular expressions.
